Architectures for workflow integration in science gateways

### 2016-04-12 paper.tex
Wrote section 4.6

@@

@@

\begin{table*}
\centering
\begin{tabular}{rcccccc}
\textbf{Metric}                      & \textbf{Tight}
                                     & \textbf{Service}
                                     & \textbf{Sub-task}
                                     & \textbf{Pool}
                                     & \textbf{Nested}
                                     & \textbf{Import} \\
\multicolumn{7}{c}{\cellcolor[HTML]{EEEEEE}\textbf{Integration}}\\
Science gateway -- \texttt{I$_1$}    & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}0  
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}2
                                     & \cellcolor[HTML]{99AA99}3 \\
Workflow engine -- \texttt{I$_2$}    & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99FF99}3 
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99FF99}1 \\
Infrastructure -- \texttt{I$_3$}   & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99FF99}0 \\
Other -- \texttt{I$_4$}              & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99AA99}3
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99FF99}0 \\
\textbf{Total}                       & \cellcolor[HTML]{99FF99}\textbf{3}
                                     & \cellcolor[HTML]{99FF99}\textbf{4}
                                     & \cellcolor[HTML]{99FF99}\textbf{2}
                                     & \cellcolor[HTML]{99AA99}\textbf{6}
                                     & \cellcolor[HTML]{99AA99}\textbf{4}
                                     & \cellcolor[HTML]{99AA99}\textbf{4} \\

@@

@@

                                     & \cellcolor[HTML]{99AA99}\textbf{9}

@@

                                     & \cellcolor[HTML]{99DD99}2

@@

@@

                                     & \cellcolor[HTML]{99FF99}\textbf{5}

@@

@@

                                     & \cellcolor[HTML]{99DD99}\textbf{20}

@@

\caption{Architecture evaluation. Lower values (brighter colors) indicate better performance. \todo{update colors and find a more relevant way to compute a grand total without favoring criteria that have more metrics than the others (e.g. normalize each criterion between 0 and 1).}}

>>>>

\todo{instantiation is for foreign workflows, i.e. 2 services. We could have another one with native workflows too.}

\todo{both workflow engines have to access the infrastructure. If they
  run on 2 infrastructures, c1 has to be duplicated.}

\todo{define parent and child engine}

@@

\subsection{Nested workflows and service invocation}

\paragraph{Integration} Setting up a nested workflow architecture with
service invocation requires interaction \texttt{d} in the science
gateway (\texttt{I$_1$=1}), and the development of 2 workflow services
with 2 instances of interactions \texttt{b} and \texttt{c$_2$}
(\texttt{I$_2$=5}).

\paragraph{Robustness} Workflow execution involves the science
gateway, 2 workflow services and the infrastructure
(\texttt{R$_1$=4}), which includes 7 interactions
(\texttt{R$_2$=7}). Debugging is difficult because the science gateway
cannot directly access fine-grained information in the sub-workflow
(\texttt{R$_3$=1}).

\paragraph{Modularity} Adding a new type of \emph{parent} engine
requires to implement the corresponding service, to implement
interactions \texttt{b} and \texttt{c$_2$} in the parent engine, and
to implement interaction \texttt{d} in the science gateway and in the
parent service (\texttt{M$_1$=5}). Adding a new type of \emph{child}
engine only requires to implement the corresponding service, to
develop interactions \texttt{b} and \texttt{c$_2$} in the child
engine, and to implement interaction \texttt{d} in the parent service
(\texttt{M$_1$=4}). We use \texttt{M$_1$=4.5} in
Table~\ref{table:evaluation} to reflect both conditions. Adding a new
version in the parent or child engine only requires modifying this
engine (\texttt{M$_2$=0}). Adding a new infrastructure requires to
re-implement interactions \texttt{b} and \texttt{c$_2$} twice, and
interaction \texttt{c$_1$} once (\texttt{M$_3$=5}). Adding a new
workflow is done through interaction \texttt{a}
(\texttt{M$_4$=1}). Meta-workflows are possible, which is one of the
main interest of this architecture (\texttt{M$_5$=0}).

\paragraph{Scalability} As in the service architecture, adding a new
workflow instance requires manual configuration in the science gateway
(instance of a parent engine), or in the parent engine (instance of a
child engine) (\texttt{S$_1$=1}). Similarly, elastic engines are
difficult to achieve (\texttt{S$_2$=1}). Distributed engines are
possible, through meta-workflows (\texttt{S$_3$=0}). Task scheduling
is more complex than in other architectures though, due to the fact
that workflow execution is split in different engines (\texttt{S$_4$=1}).

@@

\begin{table*}
\centering
\begin{tabular}{rcccccc}
\textbf{Metric}                      & \textbf{Tight}
                                     & \textbf{Service}
                                     & \textbf{Sub-task}
                                     & \textbf{Pool}
                                     & \textbf{Nested}
                                     & \textbf{Import} \\
\multicolumn{7}{c}{\cellcolor[HTML]{EEEEEE}\textbf{Integration}}\\
Science gateway -- \texttt{I$_1$}    & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}0  
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}3 \\
Workflow engine -- \texttt{I$_2$}    & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99FF99}3 
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99AA99}5
                                     & \cellcolor[HTML]{99FF99}1 \\
Infrastructure -- \texttt{I$_3$}   & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99FF99}0 \\
Other -- \texttt{I$_4$}              & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99AA99}3
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99FF99}0 \\
\textbf{Total}                       & \cellcolor[HTML]{99FF99}\textbf{3}
                                     & \cellcolor[HTML]{99FF99}\textbf{4}
                                     & \cellcolor[HTML]{99FF99}\textbf{2}
                                     & \cellcolor[HTML]{99AA99}\textbf{6}
                                     & \cellcolor[HTML]{99AA99}\textbf{6}
                                     & \cellcolor[HTML]{99AA99}\textbf{4} \\

@@

                                     & \cellcolor[HTML]{99AA99}7      

@@

                                     & \cellcolor[HTML]{99AA99}\textbf{12}

@@

                                     & \cellcolor[HTML]{99DD99}4.5

@@

                                     & \cellcolor[HTML]{99FF99}5

@@

                                     & \cellcolor[HTML]{99FF99}\textbf{10.5}

@@

                                     & \cellcolor[HTML]{99DD99}\textbf{3}

@@

                                     & \cellcolor[HTML]{99DD99}\textbf{31.5}

@@

\caption{Architecture evaluation. Lower values (brighter colors) indicate better performance. \todo{update colors and find a more relevant way to compute a grand total without favoring criteria that have more metrics than the others (e.g. normalize each criterion between 0 and 1). Same comment for each sub-total. M1 might be the same as integration.}}
